### 2020-01-22 report/02-methods.Rmd
Cleaning report

```{r, fig.cap = "Distribution of fish length. Red, green and black respectively locate the median, the mean and the 200mm threshold."}
myload(length_analysis, dir = mypath("data"))
length_analysis %>%
  ggplot(aes(x = length)) +
  geom_histogram() +
  geom_vline(xintercept = median(length_analysis$length, na.rm = TRUE), color = "red") +
  geom_vline(xintercept = mean(length_analysis$length, na.rm = TRUE), color = "green") +
  geom_vline(xintercept = 200, color = "black")
```

@@

@@

```{r pca-hab, fig.dim = c(7, 21), fig.cap = "PCA over habitat description"}
library(ade4)
library(factoextra)
pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_pressure), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)

@@

pca_plot23 <- fviz_pca_var(pca_hab,
    axes = c(2, 3),
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
plot_grid(pca_plot12, pca_plot13, pca_plot23, ncol = 1)
```

@@

```{r}
dev.off()
m <- cor(as.matrix(select(na.omit(habitat_pressure), -station)), method = "spearman")
corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
```

#### 1 rotated PCA

```{r}
evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler", "DBO_med")
evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
  "avg_depth_station_cv", "DBO_cv")
pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
  na.omit

@@

axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
p_l_rot <- map(axis_pair, 
  function (axis)
    pca_rotated_plot <- plot_rotated_pca(
      pca_rotated = pca_rotated,
      axis = axis 
    )
)
to_plot <- c(1, 6, 7)
plot_grid(plotlist = c(
    map(p_l_rot[to_plot], ~.x$rotated),
    map(p_l_rot[to_plot], ~.x$normal)
    ), ncol = length(to_plot))
```

@@

mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
```

@@

```{r split-rivers, fig.dim = c(7, 12)}
hab_type <- na.omit(habitat_pressure) %>%
  mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
  wide_bin = ifelse(width_river_mean > median(width_river_mean), TRUE, FALSE),
  hab_type = map2_chr(high_bin, wide_bin, function(high, wide){
    if (high) {
      if (wide) {
	"high_wide"
      } else {
	"high_narrow"
      }
    } else {
      if (wide) {
	"low_wide"
      } else {
	"low_narrow"
      }
    }

@@

hab_type_pca <- hab_type[hab_type$station %in% na.omit(habitat_pressure)$station, ]
match_st <- match(hab_type_pca$station, na.omit(habitat_pressure)$station)
hab_type_pca <- hab_type_pca[order(match_st), ]

pca_cat_river <- fviz_pca_ind(pca_hab, label="none", habillage=hab_type_pca$hab_type,
  , ellipse.type = "convex",
             addEllipses=TRUE, ellipse.level=0.95)
plot_grid(pca_plot, pca_cat_river, ncol = 1)
mysave(hab_type, dir = mypath("report"), overwrite = TRUE)
```

@@

```{r, echo = FALSE}
library(vegan)

@@

stressplot(nmds)
plot(nmds)

@@

bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= bluefunc(15)[findInterval(tps_com_met$richness_avg, seq(1,15))],
   cex = findInterval(log10(tps_com_met$biomass_med), seq(1, 4, 1))/2,
  air=0.01, pch = "+", labels = "+")
```

@@

plot(station_analysis[,"basin"])
# How many station by basin:
nb_st_basin <- station_analysis %>%
  group_by(basin) %>%
  summarise(nobs = n())
```

```{r basin-com}
dev.off()
match_st_basin <- match(station_analysis$station, com_mat$station)
st_basin <- 
  station_analysis[order(match_st_basin), ] %>%
  mutate(basin = ifelse(is.na(basin), "INCONNU", basin))

ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="red",air=0.01)
# See https://www.davidzeleny.net/anadat-r/doku.php/en:ordiagrams_examples
u_basin  <- unique(st_basin[["basin"]])
for (i in seq_along(u_basin)) {
  ordihull(nmds, groups = st_basin[["basin"]],
 show.group = u_basin[i], col = i, draw = 'polygon', label = T)
}
```

```{r, eval = FALSE}
match_st <- match(hab_type$station, com_mat$station)
hab_type <- hab_type[order(match_st), ]
ordiplot(nmds,type="points", choices = c(1, 2))
orditorp(nmds,display="species",col="red",air=0.01)
u_hab  <- unique(hab_type[["hab_type"]])
for (i in seq_along(u_hab)) {
  ordihull(nmds, groups = hab_type[["hab_type"]], alpha = .1,
 show.group = u_hab[i], col = i, draw = 'polygon', label = T)
}
```

```{r}
st_basin <- get_basin_station() 
myload(region_polygon, dir = mypath("data"))
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
stab_div_basin <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  select(station, troph_group, biomass_stab, richness_avg) %>%
  left_join(st_basin, by = "station") %>%
  filter(!is.na(basin))
stab_div_basin %>%
  left_join(hab_type, by = "station") %>%
  left_join(habitat_pressure[,c("station", "temperature_med", "DBO_med")],
    by = "station") %>%
  gather(variable, value, temperature_med, DBO_med) %>%
  ggplot(aes(x = richness_avg, y = value)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(variable), scales = "free_y") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    ) +
  #scale_y_log10() +
  scale_x_log10() +
  labs(title = "Stability - Div by habitat type",
    x = "Average species richness (log10)", y = "Biomass stability (log10)")
```

#### Species occurence

@@

com <- community_analysis %>%
  dplyr::select(opcod, species, biomass) %>%
  dplyr::left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  dplyr::filter(!is.na(station)) %>%
  dplyr::group_by(station) %>%
  tidyr::nest() %>%
  mutate(data = map(data, function (.data) {
      .data %<>%
	tidyr::spread(species, biomass) %>%
	dplyr::select(-opcod) %>%
	dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
	dplyr::summarise_all(list(~ sum(. != 0) / n()))
      return(.data)
      }
    )
  )
occurence_sp_st <- com %>%
  unnest()

med_occ <- occurence_sp_st %>%
  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
  gather(sp, med_occ, everything())

med_occ %>%
  ggplot(aes(x = med_occ)) +
  geom_histogram()

###### Species peripherical globally

```{r stab-sp-occ, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}
sp_per <- med_occ[med_occ$med_occ < .30,]$sp

threshold_occ <- c(.10, .30, .50, .80)
com_wo_per  <- map(threshold_occ, ~ rm_sp_from_com(com = community_analysis, sp_to_rm =
    med_occ[med_occ$med_occ < .x,]$sp))
names(com_wo_per) <- threshold_occ

com_data <- list(total = community_analysis)
com_data <- c(com_data, com_wo_per)

res_sync_per <- map2(com_data, names(com_data), function (.data, .names) {

  sync <- compute_com_synchrony(
    .op = op_analysis,
    com = .data)
  sync$type <- .names 
  sync$biomass_stab <- 1 / sync$cv_com
  return(sync)

})

test <- do.call(rbind, res_sync_per)

test %>%
  ggplot(aes(x = richness_med, y = biomass_stab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type))

```{r}
test %>%
  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
  ggplot(aes(x = log10(richness_med), y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type), rows = vars(stab))

###### Species peripherical by station

```{r, fig.dim = c(10, 7)}

threshold_occ <- c(0, .10, .30, .60, .90)

res_sync_occ_st <- map_dfr(threshold_occ, function (.threshold) {

  # List of sp to rm
  sp_to_rm <- occurence_sp_st %>%
    gather(sp, occ, -station) %>%
    group_by(station) %>%
    filter(occ < .threshold) %>%
    summarise(sp2 = list(unique(sp)))

  # Rm species by station
  truncated_com <- community_analysis %>%
    left_join(select(op_analysis, opcod, station), by = "opcod") %>%
    filter(!is.na(station)) %>%
    group_by(station) %>%
    nest() %>%
    left_join(sp_to_rm, by = "station") %>%
    mutate(
      output = map2(data, sp2, function (.data, sp_vec) {
	rm_sp_from_com(com = .data, sp_to_rm = sp_vec)
  })
      ) %>%
  unnest(output) %>%
  select(-station)

  sync <- compute_com_synchrony(
    .op = op_analysis,
    com = truncated_com)

  sync$type <- .threshold 
  sync$biomass_stab <- 1 / sync$cv_com

  return(sync)
    })

res_sync_occ_st %>%
  select(richness_tot, richness_med, biomass_stab, type) %>%
  gather(rich_type, richness, richness_med, richness_tot) %>%
  ggplot(aes(x = richness, y = biomass_stab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type), rows = vars(rich_type))
```

Removing the peripherical species nor at the global scale neither at the station
scale do not affect the stability-diversity relationship.

>>>>

```{r, fig.dim = c(4, 4), fig.cap = "Distribution of fish length. Red, green and black respectively locate the median, the mean and the 200mm threshold."}
myload(length_analysis, dir = mypath("data"))
length_analysis %>%
  ggplot(aes(x = length)) +
  geom_histogram() +
  geom_vline(xintercept = median(length_analysis$length, na.rm = TRUE), color = "red") +
  geom_vline(xintercept = mean(length_analysis$length, na.rm = TRUE), color = "green") +
  geom_vline(xintercept = 200, color = "black")
```

@@

### Network caracteristics

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)
```

```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
# Get network metrics

cor_avg <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med"))) %>%
  na.omit %>%
  cor(., method = "spearman")
#knitr::kable(cor_avg)
as.data.frame(round(cor_avg,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
cor_cv <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("cv"))) %>%
  na.omit %>%
  cor(., method = "spearman")

as.data.frame(round(cor_cv,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")

```{r}
library(ade4)
library(factoextra)

net_ind <- temporal_network_metrics %>%
  left_join(select(temporal_community_metrics, station, richness_med)) %>%
  select_at(vars(dplyr::matches("med")))

res.pca <- dudi.pca(na.omit(net_ind),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)
eig_plot <- fviz_eig(res.pca)
```

```{r}
pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})

plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], labels =
  "AUTO")
```

@@

```{r, fig.cap = "Spearman correlation between environmental variables."}
m <- cor(as.matrix(select(na.omit(habitat_pressure), -station)), method = "spearman")
corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
```

```{r pca-hab, fig.dim = c(10, 7), fig.cap = "PCA over habitat description"}
library(ade4)
library(factoextra)
pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_pressure), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)

@@

pca_plot23 <- fviz_pca_var(pca_hab,
    axes = c(2, 3),
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
plot_grid(pca_plot12, pca_plot13, pca_plot23, ncol = 3)
```

@@

```{r, fig.show = "hide"}
evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler", "DBO_med")
evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
  "avg_depth_station_cv", "DBO_cv")
pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
  na.omit

@@

axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
p_l_rot <- map(axis_pair, 
  function (axis)
    pca_rotated_plot <- plot_rotated_pca(
      pca_rotated = pca_rotated,
      axis = axis 
    )
)
```

```{r}
to_plot <- c(1, 6, 7)
plot_grid(plotlist = c(
    map(p_l_rot[to_plot], ~.x$rotated),
    map(p_l_rot[to_plot], ~.x$normal)
    ), ncol = length(to_plot), rel_height = c(.4, .6))
```

@@

mysave(habitat_pressure, pca_pressure, dir = mypath("report"), overwrite = TRUE)
```

@@

```{r split-rivers, fig.dim = c(4, 4)}
hab_type <- habitat_pressure %>%
  mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
  wide_bin = ifelse(width_river_mean > median(width_river_mean), TRUE, FALSE),
  hab_type = map2_chr(high_bin, wide_bin, function(high, wide){
    if (high) {
      if (wide) {
	"high_wide"
      } else {
	"high_narrow"
      }
    } else {
      if (wide) {
	"low_wide"
      } else {
	"low_narrow"
      }
    }

@@

#plot_grid(pca_cat_river, ncol = 1)
mysave(hab_type, dir = mypath("report"), overwrite = TRUE)
```

@@

```{r, fig.dim = c(7, 5), fig.cap = "NMDS on species composition."}
library(vegan)

@@

@@

par(mfrow = c(1, 2))
stressplot(nmds)
title("Stress plot")
bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= bluefunc(15)[findInterval(tps_com_met$richness_avg, seq(1,15))],
   cex = findInterval(log10(tps_com_met$biomass_med), seq(1, 4, 1))/2,
  air=0.01, pch = "+", labels = "+")
title("Color = species richness; Size of points = biomass")
```

@@

# How many station by basin:
nb_st_basin <- station_analysis %>%
  group_by(basin) %>%
  summarise(nobs = n())
```

```{r basin-com, fig.dim = c(7, 4), fig.cap = "Species composition by group (95% ellipse)"}
match_st_basin <- match(station_analysis$station, com_mat$station)
st_basin <- 
  station_analysis[order(match_st_basin), ] %>%
  mutate(basin = ifelse(is.na(basin), "INCONNU", basin))

par(mfrow = c(1,2))

ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="red",air=0.01)
title("Composition by basin")
# See https://www.davidzeleny.net/anadat-r/doku.php/en:ordiagrams_examples
u_basin  <- unique(st_basin[["basin"]])
for (i in seq_along(u_basin)) {
  ordiellipse(nmds, groups = st_basin[["basin"]],
 show.group = u_basin[i], col = i, draw = 'polygon', label = T)
}

tmp_hab_type <- filter(hab_type, station %in% com_mat$station)
match_st <- match(tmp_hab_type$station, com_mat$station)
tmp_hab_type <- tmp_hab_type[order(match_st), ]
ordiplot(nmds,type="points", choices = c(1, 2))
orditorp(nmds,display="species",col="red",air=0.01)
title("Composition by Low / High altitude")
u_hab  <- unique(tmp_hab_type[["hab_type"]])
for (i in seq_along(u_hab)) {
  ordiellipse(nmds, groups = tmp_hab_type[["hab_type"]], alpha = .3,
 show.group = u_hab[i], col = i, draw = 'polygon', label = T)
}
```

#### Species occurrence

@@

com <- community_analysis %>%
  dplyr::select(opcod, species, biomass) %>%
  dplyr::left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  dplyr::filter(!is.na(station)) %>%
  dplyr::group_by(station) %>%
  tidyr::nest() %>%
  mutate(data = map(data, function (.data) {
      .data %<>%
	tidyr::spread(species, biomass) %>%
	dplyr::select(-opcod) %>%
	dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
	dplyr::summarise_all(list(~ sum(. != 0) / n()))
      return(.data)
      }
    )
  )

# Local med occurence
occurence_sp_st <- com %>%
  unnest()

global_med_occ <- occurence_sp_st %>%
  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
  gather(sp, med_occ, everything())

p_global_med_occ <- global_med_occ %>%
  ggplot(aes(x = med_occ)) +
  geom_histogram() +
  labs(x = "Median occurrence of species in station")

mysave(occurence_sp_st, dir = mypath("report"), overwrite = TRUE)
```

### 2020-01-22 report/03-results.Rmd
Cleaning report

```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
# Get network metrics
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)

cor_avg <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med"))) %>%
  cor()
#knitr::kable(cor_avg)
as.data.frame(round(cor_avg,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
cor_cv <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("cv"))) %>%
  cor()
as.data.frame(round(cor_cv,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r}
library(ade4)
library(factoextra)

net_ind <- temporal_network_metrics %>%
  left_join(select(temporal_community_metrics, station, richness_med)) %>%
  select_at(vars(dplyr::matches("med")))

res.pca <- dudi.pca(na.omit(net_ind),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)
eig_plot <- fviz_eig(res.pca)
```

```{r}
pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})

plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], labels =
  "AUTO")
```

@@

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)
```

@@

### Community description

#### Temporal dynamics

```{r}
myload(community_metrics, dir = data_common)
```

```{r, fig.dim = c(10, 7)}
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
station_high_low_stab <- temporal_community_metrics %>%
  arrange(desc(biomass_stab)) %>%
  slice(c(1:5, (n() - 4):(n() - 0))) %>%
  select(station) %>%
  unlist
names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
```

```{r tmp-stab, fig.dim = c(10, 7), fig.cap = "The five lowest and highest biomass stability"}
temporal_biomass <- community_metrics %>%
  filter(station %in% station_high_low_stab) %>%
  mutate(stab_status = ifelse(
      station %in% station_high_low_stab[names(station_high_low_stab) == "low"],
      "low", "high")) %>%
  group_by(stab_status, station) %>%
  nest() %>%
  group_by(stab_status) %>%
  mutate(id_stab = seq_along(station)) %>%
  unnest()
ggplot(temporal_biomass, aes(y = biomass, x = date)) +
  geom_line() +
  geom_point() +
  facet_grid(id_stab ~ stab_status, scales = "free_y") +
  labs(y = "Biomass (g)", x = "Date")
```

```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}

# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

plot_stab <- purrr::map(station_high_low_stab, function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab, ncol = 2)
```

```{r less-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
plot_grid(plotlist = plot_stab[7:10], ncol = 2)
```

```{r mid-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
# Middle station 
plot_stab <- purrr::map(sync_sp_troph$station[209:212], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:4], ncol = 2)
```

```{r 75-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[300:304], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:4], ncol = 2)
```

```{r 25-stab-troph, eval = FALSE, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:10], ncol = 2)
```

```{r}
high_div_station <- temporal_community_metrics %>%
  arrange(desc(richness_med)) %>%
  slice(1: 5) %>%
  select(station) %>%
  unlist
```

```{r tmp-richest, fig.dim = c(10, 7), fig.cap = "The five highest rich community."}
label_stab <- filter(temporal_community_metrics,
  station %in% high_div_station) %>%
mutate(
  x_pos = ymd_hms("2005-01-01T15:00:00"),
  x_pos = as.Date(x_pos),
  y_pos = 50000,
  text = paste0("Stability: ", round(biomass_stab,2)),
)
ggplot(filter(community_metrics, station %in% high_div_station),
  aes(y = biomass, x = date)) +
  geom_line() +
  geom_point() +
  geom_text(data = label_stab, aes(x = x_pos, y = y_pos, label =
      text), size = 6) +
  facet_wrap( ~ station) + 
  labs(y = "Biomass (g)", x = "Date")
```

```{r}
myload(network_analysis, network_metrics, dir = dest_dir)
high_div_troph_group <- network_metrics %>%
  select(opcod, troph_group) %>%
  unnest() %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  left_join(select(op_analysis, opcod, station, date)) %>%
  filter(station %in% high_div_station)
```

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group,
  aes(y = nbnode, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = label_stab,
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label =
      text), size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The five richest station",
  y = "Fish species richness", x = "Date")
```

```{r}
highest_div_grp_3_station <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group == 3) %>%
  arrange(desc(richness_avg)) %>%
  slice(1:12) %>%
  select(station) %>%
  unlist()
high_div_troph_group_3 <- network_metrics %>%
  select(opcod, troph_group) %>%
  unnest() %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  left_join(select(op_analysis, opcod, station, date)) %>%
  filter(station %in% highest_div_grp_3_station)
```

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Biomass of trophic group (g)", x = "Date")
```

```{r}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Biomass of trophic group (g)", x = "Date")
```
